Towards a Classification of Isolated $j$-invariants

### 2023-09-21 TeX/author_info.tex
Updates from Overleaf

\author[Bourdon]{Abbey Bourdon}
\address{
  Abbey Bourdon,
  Wake Forest University,
  Department of Mathematics, 127 Manchester Hall, PO Box 7388, Winston-Salem, NC 27109
}
\email{\url{bourdoam@wfu.edu}}
\thanks{AB is supported by NSF Grant DMS-2145270.}

\author[Hashimoto]{Sachi Hashimoto}
\address{%
  Sachi Hashimoto,
  Max Planck Institut für Mathematik in den Naturwissenschaften,
  Inselstraße 22,
  04103 Leipzig
}
\email{\url{sachi.hashimoto@mis.mpi.de}}
\urladdr{\url{https://sachihashimoto.github.io/}}

\author[Keller]{Timo Keller}
\address{Timo Keller, Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany}
\email{keller@math.uni-hannover.de}
\urladdr{\url{https://www.timo-keller.de}}

@@

\author[Lowry-Duda]{David Lowry-Duda}
\address{%
  David Lowry-Duda, ICERM, 121 South Main Street, Box E, 11th Floor,
  Providence, RI, 02903
}
\email{\url{david@lowryduda.com}}
\urladdr{\url{https://davidlowryduda.com}}
\thanks{%
  DLD was supported by the Simons Collaboration in Arithmetic Geometry, Number
  Theory, and Computation via the Simons Foundation grant 546235.
}
\author[Morrison]{Travis Morrison}
\address{Travis Morrison, 
Virginia Tech Department of Mathematics, 
226 Stanger Street, 
24061 Blacksburg, VA USA}
\email{\url{tmo@vt.edu}}
\urladdr{\url{https://travismo.github.io/}}

\author[Najman]{Filip Najman}
\address{
Filip Najman, University of Zagreb, Bijeni\v{c}ka Cesta 30, 10000 Zagreb, Croatia
}
\email{\url{fnajman@math.hr}}
\urladdr{\url{https://web.math.pmf.unizg.hr/~fnajman/}}

>>>>

\author[Bourdon]{Abbey Bourdon}
\address{
  Abbey Bourdon,
  Wake Forest University,
  Department of Mathematics, 127 Manchester Hall, PO Box 7388, Winston-Salem, NC 27109
}
\email{\url{bourdoam@wfu.edu}}
\thanks{AB was supported by NSF Grants DMS-2145270 and DMS-1928930. Part of the work was completed while the author was in residence at the Simons Laufer Mathematical Science Institute in Berkeley, CA, during the semester of Diophantine Geometry.}

\author[Hashimoto]{Sachi Hashimoto}
\address{  Sachi Hashimoto, Department of Mathematics,
  Brown University,
  Box 1917,
  151 Thayer Street,
  Providence, RI, 02912
}
\email{\url{sachi_hashimoto@brown.edu}}
\urladdr{\url{https://sachihashimoto.github.io/}}

\author[Keller]{Timo Keller}
\address{Timo Keller, Rijksuniveriteit Groningen, Bernoulli Institute, Bernoulliborg, Nijenborgh 9, 9747 AG Groningen, The Netherlands (previously: Leibniz Universität Hannover, Institut für Algebra, Zahlentheorie und Diskrete Mathematik, Welfengarten 1, 30167 Hannover, Germany)}
\email{t.keller@rug.nl}
\urladdr{\url{https://www.timo-keller.de}}
\thanks{%
  TK was partially supported by the 2021 MSCA Postdoctoral Fellowship 01064790 -- ExplicitRatPoints.
}

@@

\author[Lowry-Duda]{David Lowry-Duda}
\address{%
  David Lowry-Duda, ICERM, 121 South Main Street, Box E, 11th Floor,
  Providence, RI, 02903
}
\email{\url{david@lowryduda.com}}
\urladdr{\url{https://davidlowryduda.com}}
\thanks{%
  DLD was supported by the Simons Collaboration in Arithmetic Geometry, Number
  Theory, and Computation via the Simons Foundation grant 546235.
}
\author[Morrison]{Travis Morrison}
\address{Travis Morrison, 
Virginia Tech Department of Mathematics, 
226 Stanger Street, 
24061 Blacksburg, VA USA}
\email{\url{tmo@vt.edu}}
\urladdr{\url{https://travismo.github.io/}}
\thanks{TM was partially supported by the Commonwealth Cyber Initiative.}

\author[Najman]{Filip Najman}
\address{
Filip Najman, University of Zagreb, Bijeni\v{c}ka Cesta 30, 10000 Zagreb, Croatia
}
\email{\url{fnajman@math.hr}}
\urladdr{\url{https://web.math.pmf.unizg.hr/~fnajman/}}
\thanks{FN is supported by the QuantiXLie Centre of Excellence, a
  project co-financed by the Croatian Government and European Union
  through the European Regional Development Fund - the Competitiveness
  and Cohesion Operational Programme (Grant KK.01.1.1.01.0004).}
